Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-07-07 tex/ms.tex
split up mean model definitions for clarity

The data we use to test our method consists of optical spectroscopy of
XX stellar clusters in M31 for which YY-band HST photometric data
exist.  The optical spectra were obtained using the fiber-fed
Hectoscpec intrument on MMT by \citet{caldwell}.  The wavelength range
of the spectra is $3700-7200 \AA$. The instrumental resolution is
$\sim 5\AA$ across the optical range \citep{fabricant13}.  Sky
subtraction happened. The data were approximately
spectrophotometrically calibrated using an average calibration vector
the night constructed from.... (MORE HERE). Figure \ref{fig:data}
shows the spectra before and after calibration for each cluster.
Discuss S/N, sky subtraction.

\subsection{Star Cluster Model}
We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by
\begin{eqnarray}\displaystyle\label{eq:MeanModel} 
\mu(\theta, \lambda_o) & = &
\frac{m_*}{4\pi d_L^2(1+z)} \, G(\lambda,\sigma) \otimes 
S(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V}  + \\
& & \sum_{i=0}^{N_l} \frac{a_i}{\sigma_e\sqrt{2\pi}} \exp(-\frac{(\lambda - \lambda_i)^2}{2\sigma_e^2})
\nonumber \\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta & \equiv & \left[ m_*, t, Z, \tau_V, \sigma_v, z, d_L, \beta,
  \{a_i\}_{i=0}^{N_l}, \sigma_e \right]
\quad ,
\end{eqnarray} where the parameters $\theta$ include 
the stellar mass $m_*$, 
effective optical depth to dust in the $V$-band $\tau_V$,
velocity dispersion or instrumental resolution $\sigma$, 
luminosity distance $d_L$, 
redshift $z$,
and amplitudes of the $N_l$ nebular and interstellar emission lines
$a_i$.

The spectrum of one solar mass of stars that formed at lookback time
$t$ with metallicity $Z$ is given by $S(\lambda, t, Z [, \beta])$
where the additional parameters $\beta$ may include details of the
population synthesis model, such as the IMF slope and adjustments to
the stellar spectra or stellar evolutionary tracks
\citep[e.g.][]{FSPS}. We will assume $\beta$ to be fixed for the
purposes of this exercise, with no loss of generality (KEEPING IMF
SLOPE CONSTANT FOR NOW).  We will also fix the shape of the
attenuation curve, $k_\lambda \equiv \tau_\lambda/\tau_V$ to the Milky
way average of \citet{CCM89} with $R_V=3.1$ and assume that $d_L$ is
known to high precision from independent methods.

Nebular emission lines (which may arise from HII regions around the
clusters or from a diffuse ionized gas) and interstellar absorption is
modeled as a sum of Gaussians of unknown amplitude $a_i$, all of the
same width $\sigma_e$ (which need not be the same as stellar
broadening $\sigma$) and with known central wavelengths $\lambda_i$.
For emission lines the amplitudes are constrained to be positive,
while for interstellar absorption (e.g. Na D and Ca K) the amplitudes
are constrained to be negative. This framework can be easily extended
to include more complex models for the nebular emission, such as
allowing line dependent widths.

>>>>

The data we use to test our method consists of optical spectroscopy of
XX stellar clusters in M31 for which YY-band HST photometric data
exist.  The optical spectra were obtained using the fiber-fed
Hectoscpec intrument on MMT by \citet{caldwell}.  The wavelength range
of the spectra is $3700-7200 \AA$. The instrumental resolution is
$\sim 5\AA$ across the optical range \citep{fabricant13}.  Wavelength
calibration happened. Sky subtraction happened. The data were
approximately spectrophotometrically calibrated using an average
calibration vector the night constructed from.... (MORE HERE). Figure
\ref{fig:data} shows the spectra before and after calibration for each
cluster.  Discuss S/N, sky subtraction.

\subsection{Star Cluster Model}
We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by
\begin{eqnarray}\displaystyle
F_{\theta^\prime}(\lambda_o) & = &
\frac{m_*}{4\pi d_L^2(1+z)} \, S(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V} \\
\nonumber \\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta^\prime & \equiv & \left[ m_*, t, Z, \tau_V, z, d_L, \beta, \right]
\quad ,
\end{eqnarray} where the
parameters $\theta^\prime$ include the stellar mass $m_*$, effective optical
depth to dust in the $V$-band $\tau_V$, luminosity distance $d_L$,
and redshift $z$.  The obsrved frame wavelengths $\lambda_o$ are
related to the restframe wavelengths $\lambda$ in the usual way.

The spectrum of one solar mass of stars that formed at lookback time
$t$ with metallicity $Z$ is given by $S(\lambda, t, Z [, \beta])$.
Here the additional parameters $\beta$ may include details of the
population synthesis model, such as the IMF slope and adjustments to
the stellar spectra or stellar evolutionary tracks
\citep[e.g.][]{FSPS}. We will assume $\beta$ to be fixed for the
purposes of this exercise, with no loss of generality (KEEPING IMF
SLOPE CONSTANT FOR NOW).  We will also fix the shape of the
attenuation curve, $k_\lambda \equiv \tau_\lambda/\tau_V$, to the Milky
way average of \citet{CCM89} with $R_V=3.1$ and assume that $d_L$ is
known to high precision from independent methods.

BDJ Discuss broadening here.  The instrumental resolution is given by $\sigma$,

Nebular emission lines (which may arise from HII regions around the
clusters or from diffuse ionized gas) and interstellar absorption
lines are modeled as a sum of Gaussians of unknown amplitude $A_\ell$,
all of the same width $\sigma_e$ (which need not be the same as
stellar broadening $\sigma$) and with known central wavelengths
$\lambda_\ell$.  For emission lines the amplitudes are constrained to be
positive, while for interstellar absorption (e.g. Na D and Ca K) the
amplitudes are constrained to be negative. This framework can be
easily extended to include more complex models for the nebular
emission, such as allowing line dependent widths and velocities.

The final mean model is then given by 
\begin{eqnarray}\label{eq:MeanModel} 
\mu(\theta, \lambda_o) &  = & (G_\sigma  \otimes F_{\theta^\prime})(\lambda) +
\sum_{\ell=0}^{N_\ell} S_\ell \\
S_\ell & = & \frac{A_\ell}{\sigma_e\sqrt{2\pi}} \exp(-\frac{(\lambda -
 \lambda_\ell)^2}{2\sigma_e^2})\\
\theta & \equiv & \left[ \{\theta^\prime\}, \sigma, \{A_\ell\}_{\ell=0}^{N_l},
  \sigma_e \right]
\quad ,
\end{eqnarray}
where $G$ represents a Gaussian of unit area, $\otimes$ indicates
convolution, and the full parameter set $\theta$ now includes the
amplitudes of the $N_l$ nebular and interstellar emission lines
$A_\ell$.  We again implicitly include the conversion from restframe
to observed frame spectra.
